Vector Representations of Linguistic Communities and Associated Models

### 2021-12-16 paper/paper1.tex
fix typo

\begin{document}
\maketitle
\begin{abstract}
  Community-level linguistic variation is a core concept in sociolinguistics.
  % but more tools are needed to study variation from a computational perspective.
  In this paper, we use computational methods to investigate how much linguistic variation corresponds with social connections between communities.
  Technically, use conditional language models to investigate linguistic variation
  across 510 online communities.
  We probe the community representations learned by the conditional language model
  and find that they are highly correlated with a social network-based 
  representation that does not use any linguistic input.
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
  Community-level linguistic variation is a core concept in sociolinguistics.
  % but more tools are needed to study variation from a computational perspective.
  In this paper, we use computational methods to investigate the degree to which  
  linguistic variation corresponds with social connections between communities.
  Technically, we use conditional language models to learn vector representations
  for 510 online communities.
  We find that they are highly correlated with a social network-based 
  representation that does not use any linguistic input.
\end{abstract}
